Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-06 edubots_surveys.Rnw
fix grammar and typos - Introduction last par

We will try to answer these questions through the analysis of questions and
answers in the two aforementioned surveys. Eventually, what we want to obtain is a series of
recommendations to make a successful deployment of chatbot technologies (and, in
some cases, general instant messaging applications) in higher education\textcolor{black}{; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be used in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from RQ3 we will also try to find best practices in the adoption of messaging platforms and they accompanying chatbots.}

The remainder of the paper is organized as follows: \textcolor{black}{first, an overview of what
current research has found about the use of messaging applications, including
chatbots, in the classroom is described}. The methodology used in the surveys is presented in
Section \ref{sec:meth}, and the results of the surveys are presented next in
Section \ref{sec:res}. Finally, we discuss these results and conclude with a
series of recommendations in the section that closes the paper.

>>>>

We will try to answer these research questions through the analysis of the two aforementioned surveys. 
Eventually, what we want to obtain is a series of
recommendations to make a successful deployment of chatbot technologies (and, in
some cases, general instant messaging applications) in higher education\textcolor{black}{; from the response to RQ1 and RQ4 we will recommend specific technologies or applications to be used in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from RQ3 we will also try to find best practices in the adoption of messaging platforms and their accompanying chatbots.}

The paper is organized as follows: \textcolor{black}{first, an overview of what
current research has found about the use of messaging applications in the classrom, including
chatbots is presented}. Next, the methodology used in the surveys is described in
Section \ref{sec:meth}, and the results of the surveys are presented in
Section \ref{sec:res}. Finally, we discuss these results and conclude with a
series of recommendations for the successful deployment of chatbots in higher education.
